---
title: "RiSE_Processing_VersionA (single subject)"
author: "Jadyn Park"
date: "10/5/2020"
output: html_document
---

### Project Setup
```{r setup, message = FALSE}
#load libraries 
rm(list = ls())
library(knitr); library(kableExtra); library(reshape2); library(tidyverse); library(dplyr); library(tables); library(hbmem)

#currently running subject
sub.id <- "3015" 

#import encoding data
encode.path <- "/Users/Jadyn/Desktop/RiseR Project/VA_3015_Part 1.csv"
encode.data <- read.csv(encode.path, header = TRUE)

#import retrieval data
retrieve.path <- "/Users/Jadyn/Desktop/RiseR Project/VA_3015_Part 2.csv"
retrieve.data <- read.csv(retrieve.path, header = TRUE)
```

### Encoding Data Summary
``` {r encoding, message = FALSE, echo = FALSE}
#record participant's IS response, whether it's 1 or 2
item.resp <- encode.data %>% group_by(ISBlockSlide.RESP) %>% summarise(count = n())
numIS = sum(item.resp[1, 2], item.resp[2, 2]) #number of IS responses
num.NoIS = 36-numIS #number of IS no responses

#record participant's Rel response, whether it's 1 or 2
rel.resp <- encode.data %>% group_by(RBlockSlide.RESP) %>% summarise(count = n())
numR = sum(rel.resp[1, 2], rel.resp[2,2]) #number of Rel responses
num.NoR = 18-numR #number of Rel no responses

numTotal = numIS + numR #number of Total responses
num.NoTotal = num.NoIS + num.NoR #number of Total no responses

#average RT of IS trials
RT.IS = mean(encode.data$ISBlockSlide.RT, na.rm = TRUE)

#average RT of R trials
RT.R = mean(encode.data$RBlockSlide.RT, na.rm = TRUE)

#total average RT
RT.Total = mean(RT.IS, RT.R)

encode.info <- rbind(numIS, num.NoIS, numR, num.NoR, numTotal, num.NoTotal, RT.IS, RT.R, RT.Total)
rownames(encode.info) <- c("# of IS Responses", "# of IS no responses", "# of R responses", "# of R no responses", "Total responses", "Total no responses", "IS average RT", "R average RT", "Total average RT")

knitr::kable(format(encode.info, digits = 6, drop0trailing = TRUE), caption = "ENCODING DATA") %>%
  kable_styling(c("striped", "bordered"))
```

### Retrieval Data Summary
##### rows 1-10 are Item Recognition (IR) practice, 11-154 are Item Recognition (AR) trials, 155-164 are Associative Recognition practice, and 165-200 are Associative Recognition trials
##### targets (Item, R, Foils) by confidence (Low, Medium, High)
``` {r rvtable, message = FALSE, echo = FALSE}
#create data frame by pulling relevant variables
data.conf <- retrieve.data %>% 
  select(CorrectResp, Image_Type, Image_Type_Confidence, Running.Trial.)

#vector below was manually added in the original excel worksheet
data.conf$IS_R_F <- c("", "", "", "", "", "", "", "", "", "", "IS_17", "F_25", "IS_32", "IS_20", "F_47", "IS_5", "F_65", "F_38", "IS_33", "R_35", "F_43", "R_8", "F_22", "F_54", "IS_15", "F_40", "F_3", "F_60", "IS_3", "R_7", "IS_10", "R_14", "F_1", "F_9", "F_62", "F_7", "F_59", "IS_16", "IS_4", "F_28", "F_18", "IS_13", "F_15", "F_36", "F_31", "F_26", "R_21", "IS_19", "F_39", "R_28", "F_64", "R_26", "R_15", "F_57", "R_23", "R_3", "R_31", "F_58", "R_12", "F_11", "F_41", "F_72" ,"R_30", "F_14", "IS_21", "F_29", "F_34", "R_20", "R_5", "R_27", "IS_35", "F_30", "R_11", "F_63", "IS_1", "IS_31", "R_13", "IS_24", "IS_29", "R_18", "IS_8", "IS_36", "F_37", "R_34", "R_36", "R_19", "IS_22", "F_35", "R_24", "R_9", "R_10", "R_4", "IS_11", "R_33", "IS_7", "F_50", "R_32", "F_70", "F_33", "F_12", "F_13", "F_66", "F_44", "IS_12", "IS_34", "F_71", "F_49", "IS_27", "F_4" ,"F_17", "F_52", "F_23", "R_2", "F_16", "IS_30", "F_2", "IS_14", "F_21", "IS_28", "F_53", "F_24", "F_6", "F_69", "F_67", "F_5", "R_1", "R_17", "R_29", "R_6", "F_48", "F_42", "IS_9", "F_51", "IS_6", "F_46", "IS_2", "IS_25", "IS_26", "F_68", "F_45", "F_8", "F_27", "R_16", "IS_23", "F_55", "F_20", "F_32", "R_25", "F_61", "F_10", "F_56", "IS_18", "R_22", "F_19", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "") 
#I hate hard coding... this looks really bad

#using above column, categorize if the trial was ITEM, R, or FOIL
data.conf$Category <- ifelse(grepl("IS", data.conf$IS_R_F),"ITEM", 
                           ifelse(grepl("R", data.conf$IS_R_F), "R",
                                  ifelse(grepl("F", data.conf$IS_R_F), "FOILS", "")
                                  )
                            )

#omit irrelevant rows
data.conf <- data.conf[data.conf$Running.Trial. == "IRTestBloc", ]

#as factor
data.conf <- data.conf %>% mutate(
  Image_Type = factor(Image_Type),
  Image_Type_Confidence = factor(Image_Type_Confidence, levels = c("High", "Med", "Low")),
  Category = factor (Category, levels = c("R", "FOILS", "ITEM")))

#create table ... I'm CERTAIN that there's better way to do this...
  #Item vs. R, Old vs. New, L vs. M vs. H Confidence 
table.conf <- data.frame(
  "OLD_L" = c(
   sum(data.conf$Category == 'ITEM' & 
      data.conf$CorrectResp == 'Correct' &
      data.conf$Image_Type == 'Old' &
      data.conf$Image_Type_Confidence == 'Low'),
    
    sum(data.conf$Category == 'R' &
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Low'),
   
    sum(data.conf$Category != 'FOILS' &
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Low'),
    
    sum(data.conf$Category == 'FOILS' & 
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'New' &
          data.conf$Image_Type_Confidence == 'Low')
  )
)

table.conf$OLD_M <- c(
  sum(data.conf$Category == 'ITEM' & 
      data.conf$CorrectResp == 'Correct' &
      data.conf$Image_Type == 'Old' &
      data.conf$Image_Type_Confidence == 'Med'),
    sum(data.conf$Category == 'R' &
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Med'),
    sum(data.conf$Category != 'FOILS' &
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Med'),
    sum(data.conf$Category == 'FOILS' & 
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'New' &
          data.conf$Image_Type_Confidence == 'Med')
)

table.conf$OLD_H <- c(
  sum(data.conf$Category == 'ITEM' & 
      data.conf$CorrectResp == 'Correct' &
      data.conf$Image_Type == 'Old' &
      data.conf$Image_Type_Confidence == 'High'),
    sum(data.conf$Category == 'R' &
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'High'),
    sum(data.conf$Category != 'FOILS' &
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'High'),
    sum(data.conf$Category == 'FOILS' & 
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'New' &
          data.conf$Image_Type_Confidence == 'High')
)

table.conf$New_L <- c(
  sum(data.conf$Category == 'ITEM' & 
      data.conf$CorrectResp == 'Incorrect' &
      data.conf$Image_Type == 'Old' &
      data.conf$Image_Type_Confidence == 'Low'),
    sum(data.conf$Category == 'R' &
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Low'),
    sum(data.conf$Category != 'FOILS' &
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Low'),
    sum(data.conf$Category == 'FOILS' & 
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'New' &
          data.conf$Image_Type_Confidence == 'Low')
)

table.conf$New_M <- c(
  sum(data.conf$Category == 'ITEM' & 
      data.conf$CorrectResp == 'Incorrect' &
      data.conf$Image_Type == 'Old' &
      data.conf$Image_Type_Confidence == 'Med'),
    sum(data.conf$Category == 'R' &
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Med'),
    sum(data.conf$Category != 'FOILS' &
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'Med'),
    sum(data.conf$Category == 'FOILS' & 
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'New' &
          data.conf$Image_Type_Confidence == 'Med')
)

table.conf$New_H <- c(
  sum(data.conf$Category == 'ITEM' & 
      data.conf$CorrectResp == 'Incorrect' &
      data.conf$Image_Type == 'Old' &
      data.conf$Image_Type_Confidence == 'High'),
    sum(data.conf$Category == 'R' &
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'High'),
    sum(data.conf$Category != 'FOILS' &
          data.conf$CorrectResp == 'Incorrect' &
          data.conf$Image_Type == 'Old' &
          data.conf$Image_Type_Confidence == 'High'),
    sum(data.conf$Category == 'FOILS' & 
          data.conf$CorrectResp == 'Correct' &
          data.conf$Image_Type == 'New' &
          data.conf$Image_Type_Confidence == 'High')
)

rownames(table.conf) <- c("TARGETS_ITEM", "TARGETS_R", "TARGETS_ALL", "FOILS")

knitr::kable(table.conf, caption = "Targets by Image Type (Old, New) and Confidence (L, M, H)") %>%
  kable_styling(c("striped", "bordered"))
```

<br><br>

## ITEM RECOGNITION
### Item Recognition Summary
``` {r retrieval, message = FALSE, echo = FALSE}
#Item Recognition Totals
IS.totals <- data.frame(
  "IS_ITEMS" = c(sum(table.conf[1, 1:3]), sum(table.conf[1, 4:6]), "N/A", "N/A", 
                 sum(table.conf[1, 1:3])/36),
  "REL_ITEMS" = c(sum(table.conf[2, 1:3]), sum(table.conf[2, 4:6]), "N/A", "N/A",
                  sum(table.conf[2, 1:3])/36),
  "FOILS" = c("N/A", "N/A", sum(table.conf[4, 1:3]), sum(table.conf[4, 4:6]),
              sum(table.conf[4, 4:6]/72)),
  "TOTAL" = c(sum(table.conf[1:2, 1:3]), sum(table.conf[1:2, 4:6]), sum(table.conf[4, 1:3]), 
              sum(table.conf[4, 4:6]), sum(table.conf[1:2, 1:3])/72)
)
rownames(IS.totals) <- c('HITS', 'MISSES', 'FALSE ALARM', 'CORRECT REJECTION', '% Correct')

knitr::kable(format(IS.totals, digits = 6, drop0trailing = TRUE), 
             caption = "Item Recognition Totals", 
             col.names = c("IS ITEMS", "REL ITEMS", "FOILS", "TOTAL")) %>%
  kable_styling(c("striped", "bordered"))

#False Alarm Rate
FAR <- 1- sum(table.conf[4, 4:6]/72)
knitr::kable(FAR, caption = "False Alarm Rate",
             col.names = "FAR") %>%
  kable_styling(c("striped", "bordered"))

#Item Recognition RTs
data.RT <- retrieve.data %>%
  select(IRTestSlide1.RT)
data.RT <- data.RT[!is.na(data.RT$IRTestSlide1), ]
data.RT <- cbind(data.conf, data.RT)

IS.Sum <- sum(data.RT[which(data.RT[ ,1] == "Correct" & data.RT[, 2] == "Old"
                  & data.RT[, 6] == "ITEM"), 7])

IS.Count <- sum(data.conf$Category == 'ITEM' & 
      data.conf$CorrectResp == 'Correct' &
      data.conf$Image_Type == 'Old')

R.Sum <- sum(data.RT[which(data.RT[ ,1] == "Correct" & data.RT[, 2] == "Old"
                  & data.RT[, 6] == "R"), 7])

R.Count <- sum(data.conf$Category == 'R' & 
      data.conf$CorrectResp == 'Correct' &
      data.conf$Image_Type == 'Old')

Total.Sum = sum(data.RT[which(data.RT[ ,1] == "Correct" & data.RT[, 2] == "Old"), 7])
Total.Count = sum(data.conf$CorrectResp == 'Correct' & data.conf$Image_Type == 'Old')

table.RT <- data.frame(
  "IS_ITEMS" = IS.Sum/IS.Count,
  "REL_ITEMS" = R.Sum/R.Count,
  "ALL_ITEMS" = Total.Sum/Total.Count
)

knitr::kable(table.RT, caption = "Item Recognition RT",
             col.names = c("IS ITEMS", "REL ITEMS" , "ALL ITEMS")) %>%
  kable_styling(c("striped", "bordered"))
```

### Z-space
``` {r items, message = FALSE, echo = FALSE}
#targets - item specific
IS_flip <- c(table.conf[1, 6], table.conf[1, 5], table.conf[1, 4],
             table.conf[1, 1], table.conf[1, 2], table.conf[1, 3])
IS_percent <- c()
  for (i in 1:6) {
    IS_percent[i] <-sum(IS_flip[i:6])/36
  }

IS_Z <- c()
  for(j in c(2:6)) {
  IS_Z[j] <- if(sum(IS_flip[j:6])/36 == 1) {
  qnorm(0.999)
} else if(sum(IS_flip[j:6])/36 == 0) {
  qnorm(0.001)
} else {
  qnorm(sum(IS_flip[j:6])/36)
}
  }

ITEM_SPECIFIC <- data.frame(IS_flip, IS_percent, IS_Z)
t_ITEM_SPECIFIC <- as.data.frame(t(ITEM_SPECIFIC))
names(t_ITEM_SPECIFIC) <- c("8", "9", "0", "1", "2", "3")
rownames(t_ITEM_SPECIFIC) <- c("Flipped", "Percentages", "Z-space")


knitr::kable(format(t_ITEM_SPECIFIC, digits = 7, drop0trailing = TRUE), caption = "TARGETS_ITEM SPECIFIC") %>%
  kable_styling(c("striped", "bordered"))

#targets - relational
R_flip <- c(table.conf[2, 6], table.conf[2, 5], table.conf[2, 4],
             table.conf[2, 1], table.conf[2, 2], table.conf[2, 3])
R_percent <- c()
  for (i in 1:6) {
    R_percent[i] <-sum(R_flip[i:6])/36
  }

R_Z <- c()
  for(j in c(2:6)) {
  R_Z[j] <- if(sum(R_flip[j:6])/36 == 1) {
  qnorm(0.999)
} else if(sum(R_flip[j:6])/36 == 0) {
  qnorm(0.001)
} else {
  qnorm(sum(R_flip[j:6])/36)
}
  }

REL <- data.frame(R_flip, R_percent, R_Z)
t_REL <- as.data.frame(t(REL))
names(t_REL) <- c("8", "9", "0", "1", "2", "3")
rownames(t_REL) <- c("Flipped", "Percentages", "Z-space")

knitr::kable(format(t_REL, digits = 7, drop0trailing = TRUE), caption = "TARGETS_RELATIONAL") %>%
  kable_styling(c("striped", "bordered"))

#targets - all
ALL_flip <- c(table.conf[3, 6], table.conf[3, 5], table.conf[3, 4],
             table.conf[3, 1], table.conf[3, 2], table.conf[3, 3])
ALL_percent <- c()
  for (i in 1:6) {
    ALL_percent[i] <-sum(ALL_flip[i:6])/72
  }

ALL_Z <- c()
  for(j in c(2:6)) {
  ALL_Z[j] <- if(sum(ALL_flip[j:6])/72 == 1) {
  qnorm(0.999)
} else if(sum(ALL_flip[j:6])/72 == 0) {
  qnorm(0.001)
} else {
  qnorm(sum(ALL_flip[j:6])/72)
}
  }

ALL <- data.frame(ALL_flip, ALL_percent, ALL_Z)
t_ALL <- as.data.frame(t(ALL))
names(t_ALL) <- c("8", "9", "0", "1", "2", "3")
rownames(t_ALL) <- c("Flipped", "Percentages", "Z-space")

knitr::kable(format(t_ALL, digits = 7, drop0trailing = TRUE), caption = "TARGETS_ALL") %>%
  kable_styling(c("striped", "bordered"))

#foils 
FOILS_flip <- c(table.conf[4, 6], table.conf[4, 5], table.conf[4, 4],
             table.conf[4, 1], table.conf[4, 2], table.conf[4, 3])
FOILS_percent <- c()
  for (i in 1:6) {
    FOILS_percent[i] <-sum(FOILS_flip[i:6])/72
  }

FOILS_Z <- c()
  for(j in c(2:6)) {
  FOILS_Z[j] <- if(sum(FOILS_flip[j:6])/72 == 1) {
  qnorm(0.999)
} else if(sum(FOILS_flip[j:6])/72 == 0) {
  qnorm(0.001)
} else {
  qnorm(sum(FOILS_flip[j:6])/72)
}
  }

FOILS <- data.frame(FOILS_flip, FOILS_percent, FOILS_Z)
t_FOILS <- as.data.frame(t(FOILS))
names(t_FOILS) <- c("8", "9", "0", "1", "2", "3")
rownames(t_FOILS) <- c("Flipped", "Percentages", "Z-space")

knitr::kable(format(t_FOILS, digits = 7, drop0trailing = TRUE), caption = "FOILS") %>%
  kable_styling(c("striped", "bordered"))
```

### Regression
``` {r reg, echo = FALSE, messages = FALSE}
dat <- data.frame("ITEM" = ITEM_SPECIFIC[, 3], "REL" = REL[,3], "ALL" = ALL[,3], "FOILS" = FOILS[,3])

#Item Specific
item.lm <- lm(ITEM ~ FOILS, data = dat) #linear model of ITEM and FOILS
item.vec <- coef(item.lm) #vector with coefficients
                  #intercept - coef(item.lm)[1]
                  #slope - coef(item.lm)[2]
item.da <- sqrt(2/1 + coef(item.lm)[2]^2)*coef(item.lm)[1] #'da' whatever this is...
item.all <- sum(ITEM_SPECIFIC$IS_flip[4:6])/36 - sum(FOILS$FOILS_flip[4:6])/72 #all hits - FA
item.hc <- ITEM_SPECIFIC$IS_flip[6]/36 - FOILS$FOILS_flip[6]/72 #HC hits - HC FA

TARG_IS <- c(coef(item.lm)[2], coef(item.lm)[1], item.da, item.all, item.hc)

#Relational
rel.lm <- lm(REL ~ FOILS, dat)
rel.vec <- coef(rel.lm)
rel.da <- sqrt(2/1 + coef(rel.lm)[2]^2)*coef(rel.lm)[1]
rel.all <- sum(REL$R_flip[4:6])/36 - sum(FOILS$FOILS_flip[4:6])/72
rel.hc <- REL$R_flip[6]/36 - FOILS$FOILS_flip[6]/72

TARG_REL <- c(coef(rel.lm)[2], coef(rel.lm)[1], rel.da, rel.all, rel.hc)

#All
all.lm <- lm(ALL ~ FOILS, dat)
all.vec <- coef(all.lm)
all.da <- sqrt(2/1 + coef(all.lm)[2]^2)*coef(all.lm)[1]
all.all <- sum(ALL$ALL_flip[4:6])/72 - sum(FOILS$FOILS_flip[4:6])/72
all.hc <- ALL$ALL_flip[6]/72 - FOILS$FOILS_flip[6]/72

TARG_ALL <- c(coef(all.lm)[2], coef(all.lm)[1], all.da, all.all, all.hc)

TARGFJ_table <- as.data.frame(cbind(TARG_IS, TARG_REL, TARG_ALL))
rownames(TARGFJ_table) <- c("Slope", "Intercept", "da", "All Hits - FA", "HC Hits - HC FA")

knitr::kable(format(TARGFJ_table, digits = 10, drop0trailing = TRUE), caption = "TARGFJ TABLE") %>%
  kable_styling(c("striped", "bordered"))

far <- (as.numeric(IS.totals[3, 3]) + 0.5)/(72+1)
is.hit <- (as.numeric(IS.totals[1, 1]) + 0.5)/(72+1)
is.disc <- is.hit - far
is.bias <- far/(1-is.hit)

TARG_IS <- c(is.hit, is.disc, is.bias)

rel.hit <- (as.numeric(IS.totals[1, 2]) + 0.5)/(72+1)
rel.disc <- rel.hit - far
rel.bias <- far/(1-rel.hit)

TARG_REL <- c(rel.hit, rel.disc, rel.bias)

all.hit <- (as.numeric(IS.totals[1, 4]) + 0.5)/(72+1)
all.disc <- all.hit - far
all.bias <- far/(1-all.hit)

TARG_ALL <- c(all.hit, all.disc, all.bias)

TARG2 <- as.data.frame(cbind(TARG_IS, TARG_REL, TARG_ALL))
rownames(TARG2) <- c("Hit Rate", "Discriminability", "Response Bias")

knitr::kable(format(TARG2, digits = 10, drop0trailing = TRUE)) %>%
  kable_styling(c("striped", "bordered"))
```

### DPSD Calculator
##### The purpose of this chunk is to replicate the Excel version of DPSD (Dual Process Signal Detection) Calculator
##### Signal detection theory: at what point are we able to detect a signal? d' = strength (signal-noise, or, the ability to discriminate signal from noise; greater the d', stronger the signal), C = stratrgy (threshold;B, D, C, Beta)

##### function dpsdProb() from 'hbmem' package (https://rdrr.io/cran/hbmem/man/dpsdProbs.html)
``` {r DPSD, echo = TRUE}
#cumulative proportion

#Example (from https://rdrr.io/cran/hbmem/man/dpsdProbs.html)
#Low r
  #dpsdProbs(.2,1,c(-1,-.5,0,.5,1))  #studied
  #dpsdProbs(0,-1,c(-1,-.5,0,.5,1)) #new

#High r
  #dpsdProbs(.6,1,c(-1,-.5,0,.5,1))  #studied
  #dpsdProbs(0,-1,c(-1,-.5,0,.5,1)) #new
```

<br><br>

## ASSOCIATIVE RECOGNITION
``` {r assoc, message = FALSE, echo = FALSE}
data.assoc <- retrieve.data %>%
  select(ARTestSlide.ACC, AR_Pair_Description, AR_Pair_Type, ARTestSlide.RT)

data.assoc <- data.assoc[!is.na(data.assoc$ARTestSlide.ACC), ]

intact.hits <- sum(data.assoc$AR_Pair_Type == "Intact" & data.assoc$ARTestSlide.ACC == 1)
reord.cm <- sum(data.assoc$AR_Pair_Type == "Reordered" & data.assoc$ARTestSlide.ACC == 1)
accuracy <- intact.hits + reord.cm

hits.rt <- sum(data.assoc[which(data.assoc[ ,1] == 1 & data.assoc[, 3] == "Intact"), 4])/(intact.hits)
reord.rt <- sum(data.assoc[which(data.assoc[ ,1] == 1 & data.assoc[, 3] == "Reordered"), 4])/(reord.cm)
acc.rt <- sum(data.assoc[which(data.assoc[ ,1] == 1), 4])/(accuracy)

t.correct <- c(intact.hits, reord.cm, accuracy)
p.correct <- c(intact.hits/18, reord.cm/18, accuracy/36)
rt.correct <- c(hits.rt, reord.rt, acc.rt)

assoc.table <- as.data.frame(cbind(t.correct, p.correct, rt.correct))
rownames(assoc.table) <- c("Intact Hits", "Reordered CM", "Accurate Totals")
colnames(assoc.table) <- c("# trials", "% Correct", "Average RT")

knitr::kable(format(assoc.table, digits = 8, drop0trailing = TRUE), caption = "Associative Recognition Totals") %>%
  kable_styling(c("striped", "bordered"))

false.item <- sum(data.assoc$AR_Pair_Type == "Reordered" & data.assoc$ARTestSlide.ACC == 0)
false.alarm.rate <- false.item/18
false.rt <- sum(data.assoc[which(data.assoc[ ,1] == 0 & data.assoc[, 3] == "Reordered"), 4])/(false.item)

falsealarms <- as.data.frame(cbind(false.item, false.alarm.rate, false.rt))
rownames(falsealarms) <- "False Alamrs"
colnames(falsealarms) <- c("# trials", "False Alarm Rate", "Average RT")

knitr::kable(format(falsealarms, digits = 8, drop0trailing = TRUE), caption = "False Alarms") %>%
  kable_styling(c("striped", "bordered"))
```

<br><br>

## Summary
``` {r summary, messages = FALSE, echo = FALSE}
```